Data Management Plan

### 2019-12-03 reviews/reply_to_reviews.md

# The behavioural economics of domestic abuse

## Unique and new big-data perspective

We bring a data science approach to the study of domestic abuse data. We use data from West Midlands Police (serving X.X million people), Lloyds Banking Group (the UK's largest retail bank with 22 million customers), and the Crime survey for England and Wales. Our approach is new and ambitious, yet eminently feasible as we already hold the necessary data. We have support from Deputy Chief constable Louisa Rolfe at West Midlands Police, who is also the National Police Chiefs' Council lead for domestic abuse. Named postdoc Trendl works as a postdoc here at Warwick and is also an employee of Lloyds Banking Group in their behavioural and data science team. We have director support from Lloyds Banking Group for the project. Applying data at this scale to the study of domestic abuse has never been done before.

No one else has or is currently proposing to take a data science view of domestic abuse. We will be the first to demonstrate how mass administrative data can be used to address domestic abuse. We have a track record in using such data for social science (see

Quispe-Torreblanca, E., & Stewart, N. (2019). Causal peer effects in police misconduct. Nature Human Behaviour. doi: 10.1038/s41562-019-0612-8 Available at https://rdcu.be/bEAue

Adams, P., Guttman-Kenney, B., Hayes, L., Hunt, S., Laibson, D., & Stewart, N. (2018). The semblance of success in nudging consumers to pay down credit card debt. Financial Conduct Authority Occasional Papers in Financial Regulation, 45. https://www.fca.org.uk/publication/occasional-papers/occasional-paper-45.pdf

Muggleton, Parpart, Newall, Leake, Gathergood, Stewart "Gambling-related harm in mass transaction data" Under review at _Nature_.) For example, in the paper on gambling we use Lloyds Banking Group transaction data from millions of invidiuals to demonstrate that gambling is associated with increased financial distress, reduced lifestyle and health outcomes, higher rates of future unemployement and disability, and higher mortality rates. This view is unique and the first ever to demonstate such associations---again complementing the traditional qualitative case-study and small survey based approach. I THINK THE GAMBLING EXAMPLE IS A GOOD EXAMPLE OF WHAT WE WILL DELIVER FOR DOMESTIC ABUSE.)

Our approach contrasts with the qualitative approach using case studies and interviews. Our findings will complement this qualitative literature. It is from this qualitative background that the reviewers appear to have come---no reviewer had expertise in data science or econometrics. Their criticism is focussed on us as new researchers in their domain and on the feasibility of the work. We mitigate the former risk by working with an advisory board and including coauthors from a domestic abuse background. We mitiage the latter risk by already holding or having access to all of the data needed for the project, with necessary data sharing and other legal agreements signed in place.

## There are factual errors in the reviews:

## There are also unreasonable suggestions:

1. Having Lloyds Banking Group as a partner in the research is a huge asset. Lloyds are the largest retail bank with 22 million customers. It is unnecessary to have data from a second retail bank. By using weighted sampling of the 22 million, we can construct any representative sample and still achieve a sample size far in excess of any every used to study domestic abuse.

2. We are aware of the issues when using police data. We are extremely familiar with the West Midlands Police data, and have worked on project is stop and search, domestic abuse, risk assessment in custody, and alcohol and police resources. We are mitigating the issues with police data by working with bank data and with CSEW data.

3. It is not possible to provide a complete review of the literature in a six page proposal. Not is it reasonable to cite studies that are not directly relevant. We are fully aware of the studies XXXXX and the ESRC funded proposal XXXXX.

4. We already have access to all relevant data. Concerns raised by reviews XXXXXX are not relevant. We hold te police data here on servers at Warwick. The CSEW is held by XXXX and academic access is straightforward. The Lloyds data are available as postdoc Trendl works inside and is employed by Lloyds Banking Group as well as Warwick. Approvals and data sharing agreements are already signed. We stated this in the proposal.

5. As the application of very large data to research in domestic abuse is novel, there is no one with a track record in domestic abuse research with the required skills in econometrics and data science to conduct this research. Requiring such a background would make it impossible to complete the research, because there is no one with such a background. See below on advisory panel.

We adopt the following adjustments in response to the reviewers:

We take the semantic point about describing children who witness male to female intimate partner violence as victims of domestic abuse. The user reviewer has made clear their views of the language used to describe such circumstances. The reviewer is clearly reluctant for this component of the research to be completed. We take an empirical perspective: It is an empirical question whether these children are at risk of future XXXXXXX, one which this proposal will answer.

We will establish an advisory board for the project, comprising a senior police officer from West Midlands Police, a senior member of the WMP Police and Crime Commissioner's Office, an academic with experience in domestic abuse, Prof Vanessa Munro, a lawyer based here at Warwick with extensive experience of domestic abuse, and a member of the charity sector (NAME CHARITY) and a survivor of domestic abuse (NOMINATED BY THE CHARITY).

We are familiar with the Walby papers on the cost of domestic abuse

We have studied the currently funded ESRC project INSERT PROJECT NAME AND PI. Our proposal is quite different and compliments this work without duplication.

### 2019-12-03 reviews/reply_to_reviews.md

Our approach contrasts with the qualitative approach using case studies and interviews. Our findings will complement this qualitative literature. It is from this qualitative background that the reviewers appear to have come---no reviewer had expertise in data science or econometrics. Their criticism is focussed on us as new researchers in their domain and on the feasibility of the work. We mitigate the former risk by working with an advisory board and including coauthors from a domestic abuse background. We mitiage the latter risk by already holding or having access to all of the data needed for the project, with necessary data sharing and other legal agreements signed in place.

## There are factual errors in the reviews:

## There are also unreasonable suggestions:

1. Having Lloyds Banking Group as a partner in the research is a huge asset. Lloyds are the largest retail bank with 22 million customers. It is unnecessary to have data from a second retail bank and would be logistically impossible for any researchers. By using weighted sampling of the 22 million, we can construct any representative sample and still achieve a sample size far in excess of any every used to study domestic abuse.

2. We are aware of the issues when using police data. We are extremely familiar with the West Midlands Police data, and have worked with WMP on projects in stop and search, domestic abuse, risk assessment in custody, and alcohol and police resources. We are mitigating the issues with police data by working with bank data and with CSEW data.

3. It is not possible to provide a complete review of the literature in a six page proposal. Not is it reasonable to cite studies that are not directly relevant. We are fully aware of the studies XXXXX and the ESRC funded proposal XXXXX. The latter focusses upon testing the existing DASH framework, and recent outputs have shown that it has little to no explanatory power for identifying at-risk individuals. Hence our proposed research to identify reliable indicative patterns in a data scientific approach and build upon the existing work.

4. We already have access to all relevant data. Concerns raised by reviews XXXXXX are not relevant. We hold the police data and CSEW data here on servers at Warwick. The Lloyds data are immediately available, as postdoc Trendl is currently working with this data, being employed by Lloyds Banking Group as well as Warwick. Approvals and data sharing agreements are already signed. We stated this in the proposal.

5. As the application of multiple, very large datasets to research in domestic abuse is novel, there is no one with the required skills in econometrics and data science who also has a substantial track record in domestic abuse research to conduct this research. Requiring such a background would make it impossible to complete the research, because no such individuals exist. We have acknowledged this from the start, hence our working closely with policing leads, and why we propose including an advisory panel.

@@

We adopt the following adjustments in response to the reviewers:

We take the semantic point about describing children who witness male to female intimate partner violence as victims of domestic abuse, noting that the act of witnessing such events is what makes them victims. The user reviewer has made clear their views of the language used to describe such circumstances. The reviewer is clearly reluctant for this component of the research to be completed. We believe this arises from a difference of perspectives: we aim to identify the risk factors for later criminal behaviour, not out of a desire to stereotype or assign blame, but to better identify vulnerable individuals. It is an empirical question, whether such individuals are more likely to commit crime later. If they are, we have a societal responsibility to offer support to help them avoid this, not to simply blame.

The reviewer is also reluctant about the investigation of certain socio-economic factors such as the effect of benefit payment systems, expressing concern about potential working class stereotypes. Their assertion is absolutely correct that domestic abuse exists in all sections of society. However, prior research shows a significant role of financial poverty, with the CSEW showing domestic abuse rates 3.5 times higher in very low income homes compared to middle and high income.

@@

We will establish an advisory board for the project, comprising a senior police officer from West Midlands Police, a senior member of the WMP Police and Crime Commissioner's Office, an academic with experience in domestic abuse, Prof Vanessa Munro, a lawyer based here at Warwick with extensive experience of domestic abuse, and a member of the charity sector (NAME CHARITY) and a survivor of domestic abuse (NOMINATED BY THE CHARITY).

We are familiar with the Walby papers on the cost of domestic abuse. We agree they are important seminal works. Our proposal builds upon their results from qualitative works and analysis of the CSEW, by integrating far more data, from more sources, and using more advanced data analytic techniques.

%We have studied the currently funded ESRC project INSERT PROJECT NAME AND PI. Our proposal is quite different and compliments this work without duplication.

### 2019-12-05 reviews/reply_to_reviews.md

# The behavioural economics of domestic abuse

## Unique and new big-data perspective

We bring a data science approach to the study of domestic abuse data. We use data from West Midlands Police (serving X.X million people), Lloyds Banking Group (the UK's largest retail bank with 22 million customers), and the Crime survey for England and Wales. Our approach is new and ambitious, yet eminently feasible as we already hold the necessary data. We have support from Deputy Chief constable Louisa Rolfe at West Midlands Police, who is also the National Police Chiefs' Council lead for domestic abuse. Named postdoc Trendl works as a postdoc here at Warwick and is also an employee of Lloyds Banking Group in their behavioural and data science team. We have director level support from Lloyds Banking Group for the project. Applying data at this scale to the study of domestic abuse has never been done before.

No one else has or is currently proposing to take a data science view of domestic abuse across multiple, diverse datasets. Other work focusses on a qualitative approach of case studies and interviews. Quantitative work in the area (such as that by Sylvia Walby which was raised by reviewers) has only incorporated a single data source (such as the CSEW, or data from a police force), and does not incorporate external data which can provide additional data on potential causes and environmental risk factors. We will be the first to demonstrate how mass administrative data can be combined from multiple sources and used to address domestic abuse. We have a track record in using such data for social science (see

Mullett, T. L., Brown, G. D. A., Fincher, C. L., Kosinski, M., & Stillwell, D. (2019). Individual-Level Analyses of the Impact of Parasite Stress on Personality: Reduced Openness Only for Older Individuals. Personality and Social Psychology Bulletin. THIS IS THE FACEBOOK DATA PAPER, SHOULD WE WORRY THAT ALL PAPERS ARE NEIL'S?

@@

Quispe-Torreblanca, E., & Stewart, N. (2019). Causal peer effects in police misconduct. Nature Human Behaviour. doi: 10.1038/s41562-019-0612-8 Available at https://rdcu.be/bEAue

Adams, P., Guttman-Kenney, B., Hayes, L., Hunt, S., Laibson, D., & Stewart, N. (2018). The semblance of success in nudging consumers to pay down credit card debt. Financial Conduct Authority Occasional Papers in Financial Regulation, 45. https://www.fca.org.uk/publication/occasional-papers/occasional-paper-45.pdf

Muggleton, Parpart, Newall, Leake, Gathergood, Stewart "Gambling-related harm in mass transaction data" Under review at _Nature_.) For example, in the paper on gambling we use Lloyds Banking Group transaction data from millions of invidiuals to demonstrate that gambling is associated with increased financial distress, reduced lifestyle and health outcomes, higher rates of future unemployment and disability, and higher mortality rates. This view is unique and the first ever to demonstrate such associations---again complementing the traditional qualitative case-study and small survey based approach. I THINK THE GAMBLING EXAMPLE IS A GOOD EXAMPLE OF WHAT WE WILL DELIVER FOR DOMESTIC ABUSE.)

Our approach contrasts with the qualitative approach using case studies and interviews. Our findings will complement this qualitative literature. It is from this qualitative background that the reviewers appear to have come---no reviewer had expertise in data science or econometrics. Their criticism is focussed on us as new researchers in their domain and on the feasibility of the work. We mitigate the former risk by working with an advisory board and including coauthors from a domestic abuse background. We mitigate the latter risk by already holding or having access to all of the data needed for the project, with necessary data sharing and other legal agreements signed and in place.

@@

## There are factual errors in the reviews:

## There are also unreasonable suggestions:

1. Having Lloyds Banking Group as a partner in the research is a huge asset. Lloyds are the largest retail bank with 22 million customers. It is unnecessary to have data from a second retail bank and would be logistically impossible for any researchers. By using weighted sampling of the 22 million, we can construct any representative sample and still achieve a sample size far in excess of any ever used to study domestic abuse.

@@

2. We are aware of the issues when using police data. We are extremely familiar with the West Midlands Police data, and have worked with WMP on projects in stop and search, domestic abuse, risk assessment in custody, and alcohol and police resources. We are mitigating the issues with police data by working with bank data and with CSEW data.

3. It is not possible to provide a complete review of the literature in a six page proposal. Not is it reasonable to cite studies that are not directly relevant. We are fully aware of the studies XXXXX and the ESRC funded proposal XXXXX. The latter focusses upon testing the existing DASH framework, and recent outputs have shown that it has little to no explanatory power for identifying at-risk individuals. Hence our proposed research to build upon this by identifying reliable indicative patterns in a data science approach.

4. We already have access to all relevant data. Concerns raised are not relevant. We hold the police data and CSEW data here on servers at Warwick. Postdoc Trendl is already working with Lloyds data, being employed by Lloyds Banking Group as well as Warwick. Approvals and data sharing agreements are already signed. We stated this in the proposal.

5. As the application of multiple, very large datasets to research in domestic abuse is novel, there is no one with the required skills in econometrics and data science who also has a substantial track record in domestic abuse research to conduct this research. Requiring such a background would make it impossible to complete the research, because no such individuals exist. We have acknowledged this from the start, hence our working closely with domestic abuse leads in the police, and why we propose including an advisory panel.

### 2019-12-05 reviews/reply_to_reviews.md

We will establish an advisory board for the project, comprising a senior police officer from West Midlands Police, a senior member of the WMP Police and Crime Commissioner's Office, an academic with experience in domestic abuse, Prof Vanessa Munro, a lawyer based here at Warwick with extensive experience of domestic abuse, and a member of the charity sector (NAME CHARITY) and a survivor of domestic abuse (NOMINATED BY THE CHARITY).

We are familiar with the Walby papers on the cost of domestic abuse. We agree they are important seminal works. Our proposal builds upon their results from qualitative works and analysis of the CSEW, by integrating far more data, from more sources, and using more advanced data analytic techniques.

%We have studied the currently funded ESRC project INSERT PROJECT NAME AND PI. Our proposal is quite different and compliments this work without duplication.

##Anna comments

###no previous experience in domestic abuse research/no collaboration with experts
not sure what's the appropriate response to this

###too data-driven/no clear theoretical framework or mention or previous studies/issues about originality as some of the questions have either been examined in the context of other countries or with a qualitative approach
we are combining data from various sources to address key questions that either have never been examined or have only been examined using one approach - fresh perspectice argument, and emphasize the importance of data driven research. The mentioned {r} [ESRC grant] (https://gtr.ukri.org/projects?ref=ES/M01178X/1) looks at improving the DASH using "more sophisticated algorithms than a traditional logistic regression framework." -- I can't find more details on this, but they seem to be only using police data, whereas we are taking a broader view by relying on the very detailed information in the CSEW as well. We are also aware of the US literature on domestic abuse victimisation risk factors (which informed our selection of explanatory variables in the proposed analyses), however, we believe that we still lack the proper evidence base for understanding domestic abuse victimisation in the Uk. Despite of the documented issues with the CSEW, it is an incredibly rich and useful source of information on domestic abuse victimisation, which has not been exploited. Combining insights from the CSEW and police data will complement and validate existing knowledge from qualitative invetsigations.

###issues with the CSEW
Walby and Towers have found issues with the CSEW - in that it underestimates the true extent of domestic abuse given that it caps the maximum number of incidents (whereas domestic abuse is often repated). We are aware of this and plan to combine CSEW data with data from other sources.

####data quality/data access issues/timescales

####"worrying" assumptions

###specific points: 
young person living at the address -- we'll know this from police records
police mis-reporting -- comparison of csew and police reports
reliability of data, ethnicity -- 
children, only a year of data //
different explanatory variables for question 1--
random forest not explaiend--
causal effects --
no domestic abuse journals--
no mention of cost--

### 2019-12-05 reviews/reply_to_reviews.md

# The behavioural economics of domestic abuse

## Unique and new big-data perspective

We bring a data science approach to the study of domestic abuse data. We use data from West Midlands Police (serving X.X million people), Lloyds Banking Group (the UK's largest retail bank with 22 million customers), and the Crime survey for England and Wales. Our approach is new and ambitious, yet eminently feasible as we already hold the necessary data. We have support from Deputy Chief constable Louisa Rolfe at West Midlands Police, who is also the National Police Chiefs' Council lead for domestic abuse. Named postdoc Trendl works as a postdoc here at Warwick and is also an employee of Lloyds Banking Group in their behavioural and data science team. We have director level support from Lloyds Banking Group for the project. Applying data at this scale to the study of domestic abuse has never been done before.

We were dismayed by the reviews. Only reviewer XXX appreciated the need for a large-scale quantitative approach in domain dominated by qualitative research. Reviewers XXX, XXX, and XXX raised issues about access to data, even though we already have access to all of the data required and stated so in the proposal.
Our approach contrasts with the qualitative approach using case studies and interviews. Our findings will complement this qualitative literature. It is from this qualitative background that the reviewers appear to have come---no reviewer had expertise in data science or econometrics. Their criticism is focussed on us as new researchers in their domain and on the feasibility of the work. We mitigate the former risk by working with an advisory board and including coauthors from a domestic abuse background. We mitigate the latter risk by already holding or having access to all of the data needed for the project, with necessary data sharing and other legal agreements signed and in place.

# Research team experience

No one else has or is currently proposing to take a data science view of domestic abuse across multiple, diverse datasets. As 199347314 describes, "most research on domestic abuse in the UK context is qualitative in nature". Quantitative work in the area has only incorporated a single data source (such as the CSEW, or data from a police force), and does not incorporate external data which can provide additional data on potential causes and environmental risk factors. We will be the first to demonstrate how mass administrative data can be combined from multiple sources and used to address domestic abuse. We have a track record in using such data for social science (see 
Mullett, T. L., Brown, G. D. A., Fincher, C. L., Kosinski, M., & Stillwell, D. (2019). Individual-Level Analyses of the Impact of Parasite Stress on Personality: Reduced Openness Only for Older Individuals. Personality and Social Psychology Bulletin. THIS IS THE FACEBOOK DATA PAPER, SHOULD WE WORRY THAT ALL PAPERS ARE NEIL'S?

@@

Quispe-Torreblanca, E., & Stewart, N. (2019). Causal peer effects in police misconduct. Nature Human Behaviour. doi: 10.1038/s41562-019-0612-8 Available at https://rdcu.be/bEAue

Adams, P., Guttman-Kenney, B., Hayes, L., Hunt, S., Laibson, D., & Stewart, N. (2018). The semblance of success in nudging consumers to pay down credit card debt. Financial Conduct Authority Occasional Papers in Financial Regulation, 45. https://www.fca.org.uk/publication/occasional-papers/occasional-paper-45.pdf

Muggleton, Parpart, Newall, Leake, Gathergood, Stewart "Gambling-related harm in mass transaction data" Under review at _Nature_.) For example, in the paper on gambling we use Lloyds Banking Group transaction data from millions of individuals to demonstrate that gambling is associated with increased financial distress, reduced lifestyle and health outcomes, higher rates of future unemployment and disability, and higher mortality rates. This view is unique and the first ever to demonstrate such associations---again complementing the traditional qualitative case-study and small survey based approach. I THINK THE GAMBLING EXAMPLE IS A GOOD EXAMPLE OF WHAT WE WILL DELIVER FOR DOMESTIC ABUSE.)

We are familiar with the Walby papers described by XXX on the cost of domestic abuse. We agree they are important seminal works. Our proposal builds upon the qualitative findings and analysis of the CSEW, by integrating far more data, from more sources, and using more advanced data analytic techniques.

# Theory

# Feasibility of the work

4. We already have access to all relevant data, as we stated in the proposal. We hold the police data and CSEW data here on servers at Warwick. Postdoc Trendl is already working with Lloyds data and is an employee of Lloyds Banking Group as well as Warwick University. Approvals and data sharing agreements are already signed. We stated that access to data is in place and so were dismayed to see the issue raised by reviewers XXX, XXX.

1. Having Lloyds Banking Group as a partner in the research is a huge asset. Lloyds are the largest retail bank with 22 million customers. It is unnecessary to have data from a second retail bank and would be logistically difficult. By using weighted sampling of the 22 million, we can construct any representative sample and still achieve a sample size far in excess of any ever used to study domestic abuse.

2. We are aware of the issues when using police data and CSEW data. For example, Walby and Towers have found that the CSEW underestimates the true extent of domestic abuse as it caps the maximum number of incidents (whereas domestic abuse is often repeated). We are extremely familiar with the West Midlands Police data, and have worked with WMP on projects in stop and search, domestic abuse, risk assessment in custody, and alcohol and police resources. We are mitigating the issues with each data set by using multiple data sets .

Walby and Towers have found issues with the CSEW - in that it underestimates the true extent of domestic abuse given that it caps the maximum number of incidents (whereas domestic abuse is often repeated). We are aware of this and plan to combine CSEW data with data from other sources.

@@

## There are factual errors in the reviews:

# The sensitive nature of the research topic

We take the semantic point about describing children who witness male to female intimate partner violence as victims of domestic abuse, noting that the act of witnessing such events is what makes them victims. The user reviewer has made clear their views of the language used to describe such circumstances. The reviewer is clearly reluctant for this component of the research to be completed. We believe this arises from a difference of perspectives: we aim to identify the risk factors for later criminal behaviour, not out of a desire to stereotype or assign blame, but to better identify vulnerable individuals. It is an empirical question, whether such individuals are more likely to commit crime later. If they are, we have a societal responsibility to offer support to help them avoid this, not to simply blame.

The reviewer is also reluctant about the investigation of certain socio-economic factors such as the effect of benefit payment systems, expressing concern about potential working class stereotypes. Their assertion is absolutely correct that domestic abuse exists in all sections of society. But note, the word class appears nowhere in the proposal---our proposed research is not about class. Prior research shows a significant role of financial poverty, with the CSEW showing domestic abuse rates 3.5 times higher in very low income homes compared to middle and high income. This is an uncomfortable fact, but ignoring it does not make it false.

# ################## Unused Text Below Here #################

@@

##Anna comments

###no previous experience in domestic abuse research/no collaboration with experts
not sure what's the appropriate response to this

###too data-driven/no clear theoretical framework or mention or previous studies/issues about originality as some of the questions have either been examined in the context of other countries or with a qualitative approach
we are combining data from various sources to address key questions that either have never been examined or have only been examined using one approach - fresh perspectice argument, and emphasize the importance of data driven research. The mentioned {r} [ESRC grant] (https://gtr.ukri.org/projects?ref=ES/M01178X/1) looks at improving the DASH using "more sophisticated algorithms than a traditional logistic regression framework." -- I can't find more details on this, but they seem to be only using police data, whereas we are taking a broader view by relying on the very detailed information in the CSEW as well. We are also aware of the US literature on domestic abuse victimisation risk factors (which informed our selection of explanatory variables in the proposed analyses), however, we believe that we still lack the proper evidence base for understanding domestic abuse victimisation in the Uk. Despite of the documented issues with the CSEW, it is an incredibly rich and useful source of information on domestic abuse victimisation, which has not been exploited. Combining insights from the CSEW and police data will complement and validate existing knowledge from qualitative invetsigations.

###issues with the CSEW
####data quality/data access issues/timescales

@@

####"worrying" assumptions

###specific points:

young person living at the address -- we'll know this from police records
police mis-reporting -- comparison of csew and police reports
reliability of data, ethnicity -- 
children, only a year of data //
different explanatory variables for question 1--
random forest not explaiend--
causal effects --
no domestic abuse journals--
no mention of cost--

### 2019-12-05 reviews/reply_to_reviews.md

# The behavioural economics of domestic abuse

## Unique and new big-data perspective

We bring a data science approach to the study of domestic abuse data. We use data from West Midlands Police (serving X.X million people), Lloyds Banking Group (the UK's largest retail bank with 22 million customers), and the Crime survey for England and Wales. Our approach is new and ambitious, yet eminently feasible as we already hold the necessary data. We have support from Deputy Chief constable Louisa Rolfe at West Midlands Police, who is also the National Police Chiefs' Council lead for domestic abuse. Named postdoc Trendl works as a postdoc here at Warwick and is also an employee of Lloyds Banking Group in their behavioural and data science team. We have director level support from Lloyds Banking Group for the project. Applying data at this scale to the study of domestic abuse has never been done before.

We were dismayed by the reviews. Only reviewer XXX appreciated the need for a large-scale quantitative approach in domain dominated by qualitative research. Reviewer 158241287 raised issues about access to data, even though we already have access to all of the data required and stated so in the proposal.
Our approach contrasts with the qualitative approach using case studies and interviews. Our findings will complement this qualitative literature. It is from this qualitative background that the reviewers appear to have come---no reviewer had expertise in data science or econometrics. Their criticism is focussed on us as new researchers in their domain and on the feasibility of the work. We mitigate the former risk by working with an advisory board and including coauthors from a domestic abuse background. We mitigate the latter risk by already holding or having access to all of the data needed for the project, with necessary data sharing and other legal agreements signed and in place.

## Research team experience

@@

## Theory

3. It is not possible to provide a complete review of the literature in a six page proposal. Not is it reasonable to cite studies that are not directly relevant. We are fully aware of the studies XXXXX and the ESRC funded proposal XXXXX. The latter focusses upon testing the existing DASH framework, and recent outputs have shown that it has little to no explanatory power for identifying at-risk individuals. Hence our proposed research to build upon this by identifying reliable indicative patterns in a data science approach.

We are familiar with the Walby papers described by XXX on the cost of domestic abuse. We agree they are important seminal works. Our proposal builds upon the qualitative findings and analysis of the CSEW, by integrating far more data, from more sources, and using more advanced data analytic techniques.

## With Data Access Secured Already, the Project is Viable

4. We already have access to all relevant data, as we stated in the proposal. We hold the police data and CSEW data here on servers at Warwick. Postdoc Trendl is already working with Lloyds data and is an employee of Lloyds Banking Group as well as Warwick University. Approvals and data sharing agreements are already signed. We stated in the proposal that access to data is already in place and so were dismayed to see the issue raised by Reviewer 158241287.

1. Having Lloyds Banking Group as a partner in the research is a huge asset. 130837269 was concerned that we are only using data from one retail bank, but this criticism is a misunderstanding. Lloyds are the largest retail bank with 22 million customers. It is unnecessary to have data from a second retail bank and would be logistically difficult. By using weighted sampling of the 22 million, we can construct any representative sample and still achieve a sample size far in excess of any ever used to study domestic abuse.

### 2019-12-05 reviews/reply_to_reviews.md

---
output:
  word_document: default
  html_document: default
---
# The behavioural economics of domestic abuse

## A data-driven approach

Our proposal offers a novel, data-driven approach to deepen our existing knowledge of domestic abuse in the UK. We use data from West Midlands Police (serving a population of 2.9 million people), Lloyds Banking Group (the UK's largest retail bank with 22 million customers), and the Crime survey for England and Wales (CSEW; the most extensive national-level survey about domestic abuse victimisation in the UK). Our approach will derive novel insights to complement the existing body of domestic abuse research in the UK, which was predominantly generated through qualitative research methods, such as case studies and interviews. It is from this qualitative background that the reviewers appear to have come, and we believe that --very carefully putting that they dont have experiences in analysis of big data ---.

For example, the reviewers pointed out that we do not discuss previous literature in detail and that our proposed research programme does not seem to be embedded in an established theoretical framework. We are familiar with the research papers mentioned by the reviewers, and these heavily influenced our proposed analyses (as our primary aim was to address gaps in the literature and complement existing knowledge using novel data sources). However, it should be recognised that it is simply not possible to provide a literature review and detailed analysis plan within the given page limits, especially given the scale of our project. We do not have a explicit theoretical framework, as our research programme is guided by data.

Our proposal focuses on

Our approach is new and ambitious,

yet eminently feasible, as we already hold the necessary data. We have support from Deputy Chief constable Louisa Rolfe at West Midlands Police, who is also the National Police Chiefs' Council lead for domestic abuse. Named postdoc Trendl works as a postdoc here at Warwick and is also an employee of Lloyds Banking Group in their behavioural and data science team. We have director level support from Lloyds Banking Group for the project. Applying data at this scale to the study of domestic abuse has never been done before.

We were dismayed by the lack of recognition regarding the unique potential of utilising these extensive datasets and derive novel, policy-relevant insights about domestic abuse.

Only reviewer appreciated the need for a large-scale quantitative approach in domain dominated by qualitative research. Reviewer 158241287 raised issues about access to data, even though we already have access to all of the data required and stated so in the proposal.
Our approach contrasts with the qualitative approach using case studies and interviews. Our findings will complement this qualitative literature. It is from this qualitative background that the reviewers appear to have come---no reviewer had expertise in data science or econometrics. Their criticism is focussed on us as new researchers in their domain and on the feasibility of the work. We mitigate the former risk by working with an advisory board and including coauthors from a domestic abuse background. We mitigate the latter risk by already holding or having access to all of the data needed for the project, with necessary data sharing and other legal agreements signed and in place.

### 2019-12-05 reviews/reply_to_reviews.md

---
output:
  word_document: default
  html_document: default
---
# The behavioural economics of domestic abuse

## A data-driven approach

Our proposal offers a novel, data-driven approach to deepen our existing knowledge of domestic abuse in the UK. We use data from West Midlands Police (serving a population of 2.9 million people), Lloyds Banking Group (the UK's largest retail bank with 22 million customers), and the Crime survey for England and Wales (CSEW; the most extensive national-level survey about domestic abuse victimisation in the UK). Our approach will derive novel insights to complement the existing body of domestic abuse research in the UK, which was predominantly generated through qualitative research methods, such as case studies and interviews. It is from this qualitative background that the reviewers appear to have come, and while all scientific reviwers have emphasized .

### 2019-12-05 reviews/reply_to_reviews.md

---
output:
  word_document: default
  html_document: default
---
# The behavioural economics of domestic abuse

## A data-driven approach

Our proposal offers a novel, data-driven approach to deepen our existing knowledge of domestic abuse in the UK. We use data from West Midlands Police (serving a population of 2.9 million people), Lloyds Banking Group (the UK's largest retail bank with 22 million customers), and the Crime survey for England and Wales (CSEW; the most extensive national-level survey about domestic abuse victimisation in the UK). Our approach will derive novel insights to complement the existing body of domestic abuse research in the UK, which was predominantly generated through qualitative research methods, such as case studies and interviews. It is from this qualitative background that the reviewers appear to have come, and while all scientific reviwers mention the importance of using a quantitative approach to study domestic abuse and exploiting the rich information in the CSEW, they do not appear to fully recognise the . Secondary data analysis

### 2019-12-05 reviews/reply_to_reviews.md

We were dismayed by the lack of recognition regarding the unique potential of utilising these extensive datasets and derive novel, policy-relevant insights about domestic abuse.

Only reviewer appreciated the need for a large-scale quantitative approach in domain dominated by qualitative research. Reviewer 158241287 raised issues about access to data, even though we already have access to all of the data required and stated so in the proposal.
Our approach contrasts with the qualitative approach using case studies and interviews. Our findings will complement this qualitative literature. It is from this qualitative background that the reviewers appear to have come---no reviewer had expertise in data science or econometrics. Their criticism is focussed on us as new researchers in their domain and on the feasibility of the work. We mitigate the former risk by working with an advisory board and including coauthors from a domestic abuse background. We mitigate the latter risk by already holding or having access to all of the data needed for the project, with necessary data sharing and other legal agreements signed and in place.

## Research team experience

Several reviewers made the point that our research team do not have previous experience in domestic abuse research. While we might not have a track record in domestic abuse research, we would like to clarify that our proposal was written in full knowledge of the relevant literature (which we unfortunately could not detail), and that our research team is fully qualified to carry out the proposed research programme, as is demonstrated by various, high-impact publications in other, policy-relevant research topics, from estimating the harm of gambling in the UK using bank transaction data (under review in  _Nature_), [peer effects in police misconduct](https://rdcu.be/bEAue), [nudging customers to increase their credit card debt repayment](https://www.fca.org.uk/publication/occasional-papers/occasional-paper-45.pdf), [and using Big Data to test evolutionary theories](https://www.ncbi.nlm.nih.gov/pubmed/31046588#:~:targetText=Individual%2DLevel%20Analyses%20of%20the%20Impact%20of%20Parasite%20Stress%20on,Openness%20Only%20for%20Older%20Individuals.&targetText=The%20parasite%20stress%20hypothesis%20predicts,and%20extraversion%2C%20but%20higher%20conscientiousness.).   
In particular, in the gambling paper we use Lloyds Banking Group transaction data from millions of individuals to demonstrate that gambling is associated with increased financial distress, reduced lifestyle and health outcomes, higher rates of future unemployment and disability, and higher mortality rates. This view is unique and the first ever to demonstrate such associations---again complementing the traditional qualitative case-study and small survey based approach.

No one else has or is currently proposing to take a data science view of domestic abuse across multiple, diverse datasets. As 199347314 describes, "most research on domestic abuse in the UK context is qualitative in nature". Quantitative work in the area has only incorporated a single data source (such as the CSEW, or data from a police force), and does not incorporate external data which can provide additional data on potential causes and environmental risk factors. We will be the first to demonstrate how mass administrative data can be combined from multiple sources and used to address domestic abuse. We have a track record in using such data for social science 
 I THINK THE GAMBLING EXAMPLE IS A GOOD EXAMPLE OF WHAT WE WILL DELIVER FOR DOMESTIC ABUSE.)

### 2019-12-05 reviews/reply_to_reviews.md

# The behavioural economics of domestic abuse

## Unique and new big-data perspective

We bring a data science approach to the study of domestic abuse data. We use data from West Midlands Police (serving X.X million people), Lloyds Banking Group (the UK's largest retail bank with 22 million customers), and the Crime survey for England and Wales. Our approach is new and ambitious, yet eminently feasible as we already hold the necessary data. We have support from Deputy Chief constable Louisa Rolfe at West Midlands Police, who is also the National Police Chiefs' Council lead for domestic abuse. Named postdoc Trendl works as a postdoc here at Warwick and is also an employee of Lloyds Banking Group in their behavioural and data science team. We have director level support from Lloyds Banking Group for the project. Applying data at this scale to the study of domestic abuse has never been done before.

We were dismayed by the reviews. Our approach contrasts with the qualitative approach using case studies and interviews. It is from this qualitative background that the reviewers appear to have come. Although the reviewers identified that there is a need for quantitative research, in a field dominated by qualitative work, they subsequently focused their reviews on qualitative models and theory. Reviewer 199347314 even suggests that a data driven approach is a negative aspect of the proposal. Something we found particularly incongruous given that this is a proposal for the Secondary Data Analysis Initiative. Furthermore, recent results from a related ESRC grant have shown that existing models such as DASH have little to no explanatory power when tested empirically, hence demonstrating the desperate need for analyses that are quantitative and data driven

The reviewers' criticism is focused on us as new researchers in their domain and on the feasibility of the work. We mitigate the former risk by working with an advisory board and including coauthors from a domestic abuse background. We mitigate the latter risk by already holding or having access to all of the data needed for the project, with necessary data sharing and other legal agreements signed and in place.

% Reviewer 158241287 raised issues about access to data, even though we already have access to all of the data required and stated so in the proposal.
